Exposing Disputed Statements on the Web

### 2009-03-28 papers/uist_thinklink/thinklink.tex
Made changes suggested by Beth

% --- Copyright notice ---
\conferenceinfo{UIST'09}{October 4-7, 2008, Victoria, BC, Canada}
\CopyrightYear{2009}
\crdata{x-xxxxx-xxx-x/xx/xxxx}

@@

\abstract
Think Link is a tool that helps a user know when information they read on a web page is disputed. As a user browses the web, Think Link highlights snippets of text that make claims that conflict with information on other web sites. If a user clicks on a highlighted snippet then Think Link will show them an argument graph showing the best evidence for and against the claim being true.

All information in Think Link is provided by users. Think Link is designed to support two usage scenarios: (i) Activists care strongly about a particular issue and combine Think Link with a search engine to find and mark places where web sites say things that they disagree with; and (ii) Sceptical Readers install Think Link as a browser extension so that they can see when things they read are disputed and find other sources that present an alternative viewpoint.

@@

The web contains a huge amount of information, but not all of this information is accurate~\cite{Mintz2002,Neumann2003,Resnik1998,Zhou2004} and some web sites present only one side of a contentious issue~\cite{Herman2002,Gentzkow2007}. If a user is to gain a broad understanding of a topic then they will need to either stick to sources that they trust to provide accurate and balanced information or spend time looking for information on other web sites that conflicts with what they have read. Even if a user tries hard to research every topic they read, they can still get caught out by claims that they had not realized were disputed.
\todo{word this better}\todo{update all screenshots}

In this paper we present Think Link, a tool that helps users discover when information they read conflicts with information on other web sites, and helps users find alternative sources that provide different points of view. When Think Link is used as a browser plugin it will highlight text that makes a disputed claim (Figure~\ref{highlight}). When a user clicks on a highlighted snippet, Think Link presents them with an argument graph that shows the best evidence for and against the claim, as voted for by other Think Link users (Figure~\ref{claimview}).

@@

Think Link relies on users to identify disputed claims, to find instances of these claims on web sites, and to vote for which sources provide the best support or opposition for a claim. 
Think Link is designed to cater to two groups of people:

@@

The design of Think Link was guided by two user studies, in which we observed the behavior of users as they perfomed tasks fitting the usage scenarios for Activist and Sceptical Reader.

@@

Think Link builds on work in several different areas. The argumentation structure influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}. The idea of highlighting information that may not be trustworthy was previously applied to Wikipedia by WikiTrust~\cite{Adler2008a}. The model of using a community to collect and filter information from a range of sources is influenced by tagging systems~\cite{Marlow2006}. The idea of gathering up a collection of snippets from web pages has been used by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.

What makes Think Link interesting is the way that it combines ideas from these different domains and applies them to the task of showing users when the information they read conflicts with information from other sources.

@@

Think Link's argument graph is inspired by Issue Based Information System (IBIS)~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Collabatorium~\cite{Klein2007}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008} model arguments as a graph of connected ideas. While the graph structure varies between tools, most tools allow one to mark a claim as supporting or opposing another claim, and allow one to mark an claim as relating to an issue.

Although Think Link's argument graph is very similar to that used by IBIS tools, it uses it for a different purpose. In Think Link the focus is on the snippets, and the purpose of the argument graph is to organize snippets, identify when snippets are disputed, and identify which snippets provide the best evidence for a particular point of view. A user is encouraged to create a new claim only when they want to group together a large number of snippets that make that claim, and a user is expected to form an opinion primarily by looking at the snippets that make that claim, rather than by looking at the argument graph itself. This differs from the normal way in which previous IBIS tools have been used. In a tool such as gIBIS~\cite{Conklin1987a} the focus is on the argument graph. A user is encouraged to break their argument down into as many separate ideas as possible and a user is expected to use the graph itself to reach a conclusion. In Think Link it is perfectly acceptable to have a claim that is not linked to any other claims or topics, but is associated with many topics --- this would not fit with the expected usage model for other IBIS tools.

Isenmann and Reuter~\cite{Isenmann1997} identify a number of problems with using IBIS tools to help people resolve disputes and make decisions. Broadly speaking, they found that opposing groups were unkeen to agree to use an IBIS tool to resolve their dispute, and that users found it difficult to properly encode a complex issue as an argument graph. We believe that while the problems they observe are important when an IBIS tool is being used for conflict modelling and resolution they are less of a problem for a tool like Think Link that is designed primarily for conflict discovery.

Cohere~\cite{Shum2008} allows a user to associate a web page with a claim in an argument graph and provides a Firefox plugin to help users do this; however Cohere and Think Link have very different models. In Cohere, when one creates a new claim one can specify one or more URLs to be used as supporting evidence. Cohere is not intended to be used as a tool to identify disputed snippets, and does not expect users to attach large numbers of web snippets to existing claims.

@@

If one sees a claim on the web that one suspects might be untrue then one can look it up on Snopes\footnote{http://snopes.com} or FactCheck\footnote{http://factcheck.org}. Snopes is a database of urban legends that the site owners have investigated to determine whether they are true or not. FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts. Think Link's database automatically imports all contentious claims identified by Snopes. FactCheck updates infrequently enough that we have been able to manually add its disputed claims to Think Link as they appear.

@@

Several tools layer an alternative navigation graph over information on the web. TextRunner~\cite{Etzioni2008} and Idea Navigation~\cite{Etzioni2008} look for instances of subject-verb-object triples on web pages and connect these together as a graph in which objects are linked by statements made about them on different web pages. ScentHighlights~\cite{Chi2005a} highlights snippets of text on a web page that are related to topics that the user has said that they are intersted in. Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books. This ``linking of quotations'' is similar in spirit to the linking of claims in Think Link.

@@

Think Link is designed to be used in two different ways. Sceptical readers browse the web and wish to be alerted when information they read conflicts with information found on other web sites. Activists scour the web for web sites that make claims that they disagree with so that they can draw the attention of sceptical readers to claims that they disagree with. The same user may act as a sceptical reader sometimes and an activist at other times.

@@

If a sceptical reader has installed the Think Link browser extension then Think Link will draw the users attention to text snippets that make or imply disputed claims by highlighting them in red (Figure~\ref{highlight}). If a user hovers their mouse over a highlighted snippet then Think Link will display a tooltip saying what the disputed claim is. If the user clicks on a highlighted snippet then Think Link will display a visualization showing the best evidence for and against the claim, where best is determined by the number of users who voted for that evidence (Figure~\ref{claimview}).

@@

In our user studies, we found that sceptical readers wanted to be able to investigate the evidence for and against a claim without having to navigate away from that claim. We thus created an interface that consists of a horizontal array of panels where each panel provides information about the item that is selected in the panel to its left. If a panel describes a disputed claim (Figure~\ref{panel}), then a user can investigate a particular piece of supporting evidence by clicking on it and looking at the information in the panel to the right. To emphasis the connection between the panels, the claim browser places an arrow next to each selected item, pointing to the panel that gives more information about that item.

@@

We found that it was important to allow the claim browser interface to be used in two different ways. When a sceptical reader is browsing a web page and sees a disputed claim they want to be able to quickly see a small popup window giving evidence for a disputed claim without having to navigate away from the page~(Figure~\ref{claimview}); however if they are interested in the claim and want to investigate the evidence for a claim in more detail then the small popup interface is too small to easily view large amounts of information and so it is preferable to use a full-window interface.

@@

Think Link's claim graph is a variant of the IBIS~\cite{Rittel1973} model. There are three types of node: snippets, claims, and topics. A snippet is a region of text taken from a web page; a claim is a statement about the world or position that one can take on some issue; a topic is an issue or concept that a claim might relate to, and a user is a person who users Think Link. Nodes are connected together by typed, directed, links. There are three link types: supports, opposes, and relates-to. A snippet or claim can support, oppose, or relate-to a claim; and any node can relate-to a topic.

Think Link uses topics to group together related claims. A topic be an issue that several claims are proposing solutions for, for example ``What should we do about global warming?''. Alternatively, it can be a thing that claims are about, for example ``Carbon Dioxide''. Think Link uses the list of page titles on Wikipedia as a seed-set for its topics and users can also add new topics from within the claim browser.

Think Link's graph model is similar to the model used by gIBIS~\cite{Conklin1987} except that we don't distinguish between an argument and a position, we allow a claim to relate-to another claim without supporting or opposing it, we merge issues with topics, we collapse gIBIS's five ways of connecting topics together and four ways of connecting a claim to an topic into a single relates-to relation. The result is a graph structure that is significantly simpler. While Think Link's graph structure is arguably less useful for the argument modelling and resolution task that gIBIS was designed for, it is sufficient for the conflict discovery and snippet organization task that Think Link's graph is intended for, and we have found that the smaller set of link and node types reduces the mential effort required to create an argument graph.

@@

Think Link does not require that a user associate a snippet with a claim at the point at which they create it. Instead, Think Link encourages a user to associate snippets with claims and topics ``in bulk'' using the claim browser interface, after they have gathered many snippets. One anticipated usage scenario for Think Link is an activist user who uses a search engine to find a large number of snippets that make a clam that they disagrees with. In this case, the user can save time by attaching all the snippets to the same claim together, rather than having to pick the same claim for each one.

@@

@@

As the argument graph grows bigger it becomes increasingly important to make sure that it stays well connected. If different users are interested in the same topic then it is easy for them to create duplicate claims or not connect claims that should be connected. Think Link tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together and allowing a user to connect them with a single click. Think Link uses the same suggestion system to allow users to connect claims to snippets, and to connect claims to other related claims.

@@

Think Link's annotation system has some privacy issues. Every time the user browses to a page, the URL is sent to the Think Link server to check whether there are any known annotations for that page. Privacy issues are reduced by the fact that the requests contain no cookies or other identifying information, and can be cached by a third-party proxy if desired; however issues still remain. In future work hope to reduce these privacy issues. One possibility is to use a hashing system similar to that used by Google Safe Browsing\footnote{http://code.google.com/p/google-safe-browsing/}.

@@

\todo{Say something about final informal evaluation}
%After the second study, we made minor changes to our user interface (described below) and performed an informal user study with people in our organization to

@@

For the first study we recruited 12 paid participants, 5 female, 7 male, aged 18 to 52. Nine participants regularly posted to a blog and the other three regularly posted comments to blogs or mailing lists. Our intention was to recruit users who fit our ``sceptical reader'' and ``activist'' personas. In our advert, we asked people to tell us what kind of information they looked at on the web, and how they shared information with others. We selected participants who looked at information that was likely to be disputed (e.g. political commentry) and said they regularly shared information with friends. We avoided applications from people who were more interested in less disputed topics like social networking or sport.

@@

Study sessions took approximately 45 minutes. Participants were seated at a single-screen workstation with the Firefox browser augmented with the Think Link extension. We first demonstrated Think Link's interface, and then asked them to browse web sites they normally use

@@

For the second study, we recruited 6 paid participants, 4 female, 2 male. Four participants had a blog. Although we recruited participants using the same advert as the first study, the timing of our second advert around the beginning of the local university semester meant that five of the participants were college students.

@@

\subsubsection{High-Level Impressions}

Response was generally positive, with many participants being very keen to use the tool soon. One participant said ``I can see myself getting addicted to this'', and several participants asked as to notify them when it is properly deployed. Most of the participants expressed an interest in using the tool, with some wanting to use it now, and others wanting to use it ``when it is more mature''.

Most participants said that they would want to use Think Link to tell them when information they read was disputed (sceptical reader). One participant said ``The web needs to be taken with a grain of salt, and this gives you salt goggles''. A smaller number said they would want to marking up claims they disagreed with (activist). One participant who was a political blogger was very excited about the ability to mark up things he thought were lies.

Most participants in the first study, and all participants in the second study were able to use the tool competently. Participants in the second study were able to use Think Link competently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant. One participants said they found the tool ``very intuitive''.

@@

Several users got confused by claims that referred to similar events at different points in time. For example, one participant in the first study marked a two claims as opposing each other when each was true at the time that it was written. This is a particular problem when talking about breaking news events, where what claims are true can change fast. If Think Link is to be effective for describing such events then it is likely that it will need to have better support for identifying the time at which a claim was asserted to be true.

@@

The first two versions of Think Link used a drag-and-drop interface to allow a user to create links between claims. In the first interface (Figure~\ref{oldbrowser}) a user could use a search box to find other claims and then drag them into an appropriate position in the argument tree. In the second interface (Figure~\ref{secondbrowser}), followed a file-manager metaphor, providing two identical browser windows that a user could drag and drop claims between. In both cases, we found that users would often not intially realize they could use drag and drop to organize claims, even when we added a prominent information message at the top of the display (Figure~\ref{secondbrowser}). We believe that part of the problem was that users are not used to using drag-and-drop in a web interface, and there was no visible clue in the rendering of the claim graph that they could use drag and drop to create connections. In the final interface we resolved this issue by having the connection actions (``add claim'' etc) explicitly visible in the interface.

@@

We have introduced the idea of enhancing the browsing interface by highlighting snippets of text that make disputed claims and allowing a user to see an argument graph that presents the best evidence on either side of the issue. Think Link allows users to navigate between pages based on the factual claims made on pages, rather than being restricted to the links provided by authors. It allows users to identify disputed claims on web pages and connect them directly to the arguments that those claims are part of, and related claims on other web sites.

On a practical level, Think Link works by allowing users to pick out snippets on pages that make claims that they think are interesting or controversial, and then using a collaborative filtering model to allow users to vote for the most interesting evidence and structure claims into a coherent argument graph.

>>>>

% --- Copyright notice ---
\conferenceinfo{UIST'09}{October 4-7, 2009, Victoria, BC, Canada}
\CopyrightYear{2009}
\crdata{x-xxxxx-xxx-x/xx/xxxx}

@@

\abstract
Think Link is a tool that helps a user know when information they read on a web page is disputed. As a user browses the web, Think Link highlights snippets of text that make claims that conflict with information on other web sites. If a user clicks on a highlighted snippet, Think Link will display an argument graph showing the best evidence for and against the claim the snippet is making.

Users provide all Think Link's information: they create new claims, mark new snippets, connect claims and snippets together.
Think Link is designed to support two primary usage scenarios: (i) Activists care strongly about a particular issue and combine Think Link with a search engine to find and mark snippets that make claims that they disagree with; and (ii) Sceptical Readers install Think Link as a browser extension to see when statements they read are disputed and find other sources tha tpresent alternative viewpoints.

@@

\todo{update screenshots}

The web contains a huge amount of information, but some web sites contain innaccurate information~\cite{Mintz2002,Neumann2003,Resnik1998,Zhou2004} and some present only one side of a contentious issue~\cite{Herman2002,Gentzkow2007}. 
If a user is to gain a broad understanding of a topic then they will need to either stick to sources that they trust to provide accurate and balanced information or spend time looking for information on other web sites that conflicts with what they have read. 
Even if a user tries to be careful they can still be caught out by claims that they had not realized were disputed.
\todo{word this better}\todo{update all screenshots}

In this paper we present Think Link, a tool that helps users discover when information they read is disputed, and helps users find sources with alternative points of view. When Think Link is used as a browser plugin it will highlight snippets of text that makes disputed claims (Figure~\ref{highlight}). When a user clicks on a highlighted snippet, Think Link presents them with an argument graph that shows the best evidence for and against the claim (Figure~\ref{claimview}).

@@

Think Link relies on users to identify disputed claims, to find instances of these claims on web sites, and to vote for which sources provide the best support or opposition for a claim. 
Think Link is designed to cater to two primary usage scenarios:

@@

The design of Think Link was guided by two user studies in which we observed users' behaviour as they perfomed tasks fitting the usage scenarios for Activist and Sceptical Reader.

@@

Think Link builds on work in several different areas. The argumentation structure is influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}. The idea of highlighting potentially unstrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}. Tagging Systems~\cite{Marlow2006} influenced the way Think Link uses the community to collect and filter information. Clipping tools such as Internet Scrapbook~\cite{Sugiura1998} allow users to mark snippets on web sites.

What makes Think Link interesting is the way that it combines ideas from these different domains and applies them to the task of showing users when the information they read conflicts with information from other sources.
\todo{rewrite this?}

@@

Think Link's argument graph is inspired by Issue Based Information System (IBIS)~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}. IBIS tools model debate as a graph of connected issues, positions, and arguments. While the graph structure varies between tools, most tools allow a node to support or oppose another node and allow a node to be linked to an issue.

Although Think Link's argument graph is very similar to that used by IBIS tools, it uses it for a different purpose. In Think Link the focus is on the snippets, and the purpose of the argument graph is to organize snippets, identify when snippets are disputed, and identify which snippets provide the best evidence for a particular point of view. A user is encouraged to create a new claim only when they want to group together a large number of snippets that make that claim. A Think Link user is expected to form an opinion primarily by looking at the snippets listed as evidence, rather than by looking at the argument graph itself. This differs from the normal way in which previous IBIS tools have been used. In a tool such as gIBIS~\cite{Conklin1987a}, the focus is on the argument graph. A user is encouraged to break their argument down into as many separate ideas as possible and users are expected to use the graph itself to reach a conclusion. In Think Link it is perfectly acceptable to have a claim that is not linked to any other claims or topics, but is associated with many snippets --- this would not fit with the expected usage model for other IBIS tools.

Isenmann and Reuter~\cite{Isenmann1997} identify a number of problems with using IBIS tools to help people resolve disputes and make decisions. Broadly speaking, they found that opposing groups were unkeen to agree to use an IBIS tool to resolve their disputes, and that users found it difficult to properly encode a complex issue as an argument graph. We believe that while the problems they observe are important when an IBIS tool is being used for conflict modelling and conflict resolution, they are less of a problem for a tool like Think Link that is designed primarily for conflict discovery.

Cohere~\cite{Shum2008} allows a user to specify one or more URLs as evidence when creating a new claim and provides a Firefox plugin to help a user create a claim based on the page they are browsing; Cohere works with URLs rather than snippets and does not allow one to associate a new URL with an existing claim written by someone else. Cohere is not designed to be used to identify snippets on web pages that make disputed claims.

@@

If one sees a claim on the web that one suspects might be untrue then one can look it up on Snopes\footnote{http://snopes.com} or FactCheck\footnote{http://factcheck.org}. Snopes is a database of urban legends that the site owners investigated to determine whether they are true. 
Think Link's database automatically imports all contentious claims identified by Snopes.
FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts.

%FactCheck updates infrequently enough that we have been able to manually add its disputed claims to Think Link as they appear.

@@

Several tools layer an alternative navigation graph over information on the web. TextRunner~\cite{Etzioni2008} and Idea Navigation~\cite{Etzioni2008} look for instances of subject-verb-object triples on web pages and connect these together as a graph in which objects are linked by statements made about them on different web pages. ScentHighlights~\cite{Chi2005a} highlights snippets of text that relate to topics the user has expressed interest in. Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books. This ``linking of quotations'' is similar in spirit to the linking of claims in Think Link.

@@

Think Link is designed to be used in two different ways. Sceptical wish to be alerted when information they read on the web conflicts with information on other web sites. Activists scour the web for web sites that make claims that they disagree with so that they can draw the attention of sceptical readers to claims that they disagree with. The same user may act as a sceptical reader sometimes and an activist at other times.

@@

If a sceptical reader has installed the Think Link browser extension, Think Link will draw the users attention to text snippets that make or imply disputed claims by highlighting them in red (Figure~\ref{highlight}). If a user hovers their mouse over a highlighted snippet then Think Link displays a tooltip giving the disputed claim. Clicking on a highlighted snippet reveals a visualization showing the best evidence for and against the claim, as determined by the user community (Figure~\ref{claimview}).

@@

In our user studies, we found that sceptical readers wanted to be able to investigate the evidence for and against a claim without having to navigate away from that claim. We thus created an interface that consists of a horizontal array of panels where each panel provides information about the item that is selected in the panel to its left. If a panel describes a disputed claim (Figure~\ref{panel}), then a user can investigate a particular piece of supporting evidence by clicking on it and looking at the information in the panel to the right. 
To emphasize the connection between the panels, the claim browser places an arrow next to each selected item, pointing to the panel that gives more information about that item.

@@

We found that it was important to allow the claim browser interface to be used in two different ways. When a sceptical reader is browsing a web page and sees a disputed claim, they want to be able to quickly see a small popup window giving evidence for a disputed claim without having to navigate away from the page~(Figure~\ref{claimview}); however if they are interested in the claim and want to investigate the evidence for a claim in more detail, it is preferable to use a full-window interface, as the small popup interface is too small to easily view large amounts of information.

@@

Think Link's claim graph is a variant of the IBIS~\cite{Rittel1973} model. There are three types of node: snippets, claims, and topics. A snippet is a region of text taken from a web page; a claim is a statement about the world or position that one can take on some issue; and a topic is an issue or concept that a claim might relate to.. Nodes are connected together by typed, directed, links. There are three link types: supports, opposes, and relates-to. A snippet or claim can support, oppose, or relate-to a claim; and any node can relate-to a topic.

Think Link uses topics to group together related claims. A topic may be an issue that several claims are proposing solutions for, for example ``What should we do about global warming?''. Alternatively, it can be something claims are about, for example ``Carbon Dioxide''. Think Link uses the list of page titles on Wikipedia as a seed-set for its topics and users can also add new topics from within the claim browser.

Think Link's graph model is a simpler than that used by gIBIS~\cite{Conklin1987}: we don't distinguish between an argument and a position, we allow a claim to relate-to another claim without supporting or opposing it, we merge issues with topics, we collapse gIBIS's five ways of connecting issues together and four ways of connecting a claim to an issue into a single relates-to relation. While Think Link's simplified graph structure is arguably less useful for the argument modelling and resolution task that gIBIS was designed for, it is sufficient for the conflict discovery and snippet organization task that Think Link's graph is intended for, and we have found that the smaller set of less precise link and node types reduces the mental effort required to create an argument graph.

@@

Think Link does not require that a user associate a snippet with a claim at the point at which they create it. Instead, Think Link encourages a user to associate snippets with claims and topics ``in bulk'' using the claim browser interface, after they have gathered many snippets. 
One anticipated usage scenario for Think Link is an activist user who uses a search engine to find a large number of snippets that make a claim that they disagrees with. 
In this case, the user can save time by first collecting all their snippets, and then attaching all their snippets to their disputed claim in bulk.

@@

Think Link uses the same suggestion system to suggest connections between claims. It is important to make sure that the argument graph stays well connected as it grows. If users create duplicate claims or don't connect their claims to existing claims then then graph becomes less useful. Think Link tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together and allowing a user to enable a suggested connection with a single click.

@@

@@

Think Link's annotation system has some privacy issues. Every time the user browses to a page, the URL is sent to the Think Link server to check whether there are any known annotations for that page. 
Think Link reduces privacy issues by not sending cookies or other identifying information, and Think Link's requests can be cached by a third-party proxy if desired. 
In future work we hope to reduce these privacy issues. One possibility is to use a hashing system similar to that used by Google Safe Browsing\footnote{http://code.google.com/p/google-safe-browsing/}.

@@

These studies identified some usability problems which we responded to with changes to the user interface which we describe below. We conducted a lightweight evaluation of our final interface and it seemed our revisions successfully addressed the usability concerns.

\todo{Test with at least 4 people}
\todo{Say something about final informal evaluation}
%After the second study, we made minor changes to our user interface (described below) and performed an informal user study with people in our organization to

@@

For the first study we recruited twelve paid participants, five female, seven male, aged 18 to 52. Nine participants regularly posted to a blog. We recruited participants by posting an advert on craigslist\footnote{http://craigslist.org}.
Our intention was to recruit users who fit our ``sceptical reader'' and ``activist'' personas. In our advert, we asked people to tell us what kind of information they looked at on the web, and how they shared information with others. We selected participants who looked at information that was likely to be disputed (e.g. political commentry) and said they regularly shared information with friends. We avoided applications from people who were more interested in less disputed topics like social networking or sport.

@@

Study sessions took approximately fourty five minutes. Participants were seated at a single-screen workstation with the Firefox browser augmented with the Think Link extension. We first demonstrated Think Link's interface, and then asked them to browse web sites they normally use

@@

For the second study, we recruited six paid participants, four female, two male. Four participants had a blog. Although we recruited participants using the same advert as the first study, the timing of our second advert around the beginning of the local university semester meant that five of the participants were college students.

@@

% \subsubsection{High-Level Impressions}
% 
% Response was generally positive, with many participants being very keen to use the tool soon. One participant said ``I can see myself getting addicted to this'', and several participants asked as to notify them when it is properly deployed. Most of the participants expressed an interest in using the tool, with some wanting to use it now, and others wanting to use it ``when it is more mature''.
% 
% Most participants said that they would want to use Think Link to tell them when information they read was disputed (sceptical reader). One participant said ``The web needs to be taken with a grain of salt, and this gives you salt goggles''. A smaller number said they would want to mark up claims they disagreed with (activist). One participant who was a political blogger was very excited about the ability to mark up things he thought were lies.
% 
% Most participants in the first study, and all participants in the second study were able to use the tool competently. Participants in the second study were able to use Think Link competently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant. One participants said they found the tool ``very intuitive''.

@@

Several users got confused by claims that referred to similar events at different points in time. 
For example, one participant in the first study marked a two claims as opposing each other when each was true at the time that it was written. This is a particular problem when talking about breaking news events, where the facts can change fast. If Think Link is to be effective for describing such events then it will need to have better support associating times with claims and snippets.

@@

The prototype versions of Think Link used a drag-and-drop interface to allow a user to create links between claims. In the first interface (Figure~\ref{oldbrowser}) a user could use a search box to find others claims and then drag them into appropriate positions in the argument graph. The second interface (Figure~\ref{secondbrowser}) followed a file-manager metaphor, providing two identical browser windows that a user could drag and drop claims between. 
In both cases, we found that users would often not realize they could use drag and drop to organize claims, even when we added a prominent information message at the top of the display (Figure~\ref{secondbrowser}). We believe that part of the problem was that users are not used to using drag-and-drop in a web interface, and the rendering of a claim did not have any visual clue to suggest that they could use drag and drop to create connections. In the final interface we resolved this issue by having the connection actions (``add claim'' etc) explicitly visible in the interface.

@@

We have introduced the idea of enhancing the browsing interface by highlighting snippets of text that make disputed claims and allowing a user to see an argument graph that presents the best evidence on all sides of the issue. Think Link allows users to navigate between pages based on the factual claims made on pages, rather than being restricted to the links provided by web page authors. 
Users can identify snippets that make disputed pages, connect those snippets to the appropriate claims, and connect claims that relate to each other.

Think Link works by allowing users to pick out snippets on pages that make claims that they think are interesting or controversial, and then uses a collaborative filtering model to allow users to vote for the most interesting evidence and structure claims into a coherent argument graph.
